%-------------------------
% Resume in Latex
% Template author : Sourabh Bajaj
% Author: Rafael Bellotti
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{color}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{blue}
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/rafbel}{\color{blue}\Large Rafael Cortez Bellotti de Oliveira}} & \color{blue}Email : \href{mailto:bellotti.rafael@gmail.com}{\color{blue}bellotti.rafael@gmail.com}\\
  \href{https://github.com/rafbel}{\color{blue}https://github.com/rafbel} & \color{blue}Mobile : +55 21 99948-0699 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Objective}
    \resumeSubHeadingListStart
        Work for a company that values user experience, quality of service, and involves its members and community to produce engaging and collaborative solutions.
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Federal University of Rio de Janeiro}{Rio de Janeiro, Brazil}
      {Bachelor of Electronic and Computer Engineering;  CRA: 7.7}{Jan. 2012 - Jul. 2017}
    \resumeSubheading
      {Lehigh University}{Bethlehem, USA}
      {Science without Borders Exchange Student;  GPA: 3.67}{Aug. 2015 - May. 2016}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Recent Experience}
  \resumeSubHeadingListStart
	\resumeSubheading
      {Valid}{S\~ao Paulo, Brazil}
      {Systems Development Analyst}{Dec. 2017 - Present}
      \resumeItemListStart
        \resumeItem{Engagement Manager}
          {Digital marketing platform for sending e-mails and SMS. Equipped with its own editors and analytics platform, it provides all the right tools for engaging desired targets. Example clients: Guitar Center and Trader Joe's. Developed using Java, Spring Framework, Swagger, QueryDSL, Hibernate, JavaScript, Angular.js, SASS, MongoDB, PostgreSQL, Liquibase, and Bootstrap. Also used tools like Bower, NPM, Gulp, and Jenkins. }
      \resumeItemListEnd
      
      \resumeSubheading
      {Zesto}{S\~ao Paulo, Brazil}
      {Co-founder}{July 2018 - Present}
      \resumeItemListStart
        \resumeItem{Denouncement Portal}
          {Currently playing the role of project manager and architect during the development of a portal that allows companies to receive anonymous denouncements. Developed using Angular, TypeScript, Bootstrap, Java, Spring Framework, QueryDSL, Hibernate, Flyway, and MySQL.  }
      \resumeItemListEnd
      
    \resumeSubheading
      {TOTVS}{Rio de Janeiro, Brazil}
      {Mobile Developer and Squad Leader}{Sep. 2017 - Dec. 2017}

    		\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     			 \textit{\small Mobile Development Intern} & \textit{\small Jul. 2016 - Aug. 2017}\\
            \end{tabular*}\vspace{-5pt}
      \begin{comment}
            {Information Technology Development Intern}{Jul. 2016 - Aug. 2017}
	  \end{comment}
      \resumeItemListStart
          \resumeItem{Por Dentro}
          {Mobile app for Rede Globo's equity and service division. Developed using JavaScript and Appcelerator Titanium.}
        \resumeItem{Codemig}
          {App solution for Codemig to ensure ticket control at bus station. Developed using C\# and .NET.}
      \resumeItemListEnd

    \resumeSubheading
      {Lehigh University}{Bethlehem, USA}
      {Software Engineering Course Grader}{Jan. 2016 - May 2016}

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Recent Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Pet Feeder}
      {Automatic domestic pet feeder that can be activated remotely. Developed using Raspberry Pi 2 and Python for the feeder system, and Java and Swing for the client interface. }
    \resumeSubItem{Maze Runner}
      {Robot that receives instructions via Bluetooth on how to complete the maze after a photo from the maze is processed by a PC. Developed using Arduino, C++, and OpenCV.}
  \resumeSubHeadingListEnd
  
 %--------Certifications------------ 
\section{Certifications}
\resumeSubHeadingListStart
   \item{
      \textbf{Software Product Management Specialization}{: University of Alberta, March 2018}
      \hfill
   }
   \item{
      \textbf{Software Processes and Agile Practices}{: University of Alberta, December 2017}
      \hfill
   }
   \item{
      \textbf{Design Thinking for Innovation}{: University of Virginia, December 2017}
      \hfill
   }
   \item{
      \textbf{Actions and Creative Endeavors on the Web}{: UFRJ, November 2014}
      \hfill
   } 
   \item{
      \textbf{Certificate in Advance English}{: Cambridge English Language Assessment, August 2009}
      \hfill
   }  
 \resumeSubHeadingListEnd
%--------Languages------------
\section{Language Fluency}
  \resumeSubHeadingListStart
    Studied at an international school in Argentina for four and a half years (Asociaci\'on Escuelas Lincoln), where became fluent in both \textbf{English} and \textbf{Spanish}. Also fluent in my native language, \textbf{Portuguese}.
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
